On the adhesivity properties of equivalence graphs\thanks{???????}

### 2025-02-12 calco/Hypergraphs_with_equivalences.tex
Roba su funtore quoziente

\begin{proof}
    Preserve from \Cref{th:adjoints_preserves_lim}. Remain to see Reflect.
	Let $D: \cat I \to \EqHyp$ be a diagram, and let $((c_i)_{i\in \cat I}, \mathcal{C})$ be the colimit of $Q \circ D$, where $\mathcal{C} = (A, C, q\circ s, q\circ t)$, and $D(i)$ is $(A_i, B_i, C_i, s_i, t_i, q_i)$.
	Let now $T: \EqHyp \to \Set$ be the functor mapping each graph with equivalence onto its second component, $T((X, Y, Z, x, y, z)) = Y$, and each morphims onto its second component.
	Let then $((b_i)_{i\in \cat I}, B)$ be the colimit of $T \circ D$.
	Consider the following situation.
	\[\begin{tikzcd}[row sep = 24, column sep = 24]
		& B & \\
		B_i \ar[ur, "{b_i}"] \ar[rr, "h_V"] \ar[d, "{q_i}"] & & B_j \ar[ul, "{b_j}"swap] \ar[d, "{q_j}" swap] \\
		C_i \ar[dr, "{c_C^i}" swap] \ar[rr, "{h_C}"swap] & & C_j \ar[dl, "{c_C^j}"] \\
		& C &
	\end{tikzcd}\]

>>>>

\begin{proof}
    Since $Q$ is a left adjoint, it preserves colimits.
	Let $D: \cat I \to \EqHyp$ be a diagram, and let $\mathcal{C}$, together with  $(c_i)_{i\in \cat I}$ be the colimit of $Q \circ D$, where $\mathcal{C} = (A, C, q\circ s, q\circ t)$, and $D(i)$ is $(A_i, B_i, C_i, s_i, t_i, q_i)$.
	\iffalse
	Let now $T: \EqHyp \to \Set$ be the functor mapping each graph with equivalence onto its second component, $T((X, Y, Z, x, y, z)) = Y$, and each morphims onto its second component.\fi
	Let $((b_i)_{i\in \cat I}, B)$ be the colimit of $U_\EqHyp \circ D$.
	Consider the following situation.
	\[\xymatrix{

	}\]
	\[\begin{tikzcd}[row sep = 24, column sep = 24]
		& B & \\
		B_i \ar[ur, "{b_i}"] \ar[rr, "h_V"] \ar[d, "{q_i}"] & & B_j \ar[ul, "{b_j}"swap] \ar[d, "{q_j}" swap] \\
		C_i \ar[dr, "{c_C^i}" swap] \ar[rr, "{h_C}"swap] & & C_j \ar[dl, "{c_C^j}"] \\
		& C &
	\end{tikzcd}\]
